---
title: "Week 6 lecture"
author: "Mei Iwamoto"
format: html
editor: visual
---

## How to add code chunks 
(green button above) or command option i
```{r}
#see code chunk here
```

code chunk options: add a #| in the chunk to control what you want printed in the chunk, like #| warning: false
```{r}
#| warning: false 
#warning: false is typed here but you canʻt see it in the output file 

#this prevents warnings from printing for this chunk only, if you want to apply it to the whole doc, add it to the very top
```
or like this to add defaults at the top of your doc: 

execute:
  warning: false   # suppress warnings in all chunks
  message: false   # suppress package loading messages
  echo: false      # hide code by default (show results only)
  eval: true       # run all chunks (the default)

## Use inline r code rather than manually typing numbers 

so that numbers can automatically update when you run things/things are more reproducible 

```{r}
# In your prose (not a code chunk), write:
# backtick + r + space + expression + backtick, not apostrophe!!

# Examples:
# The dataset has `nrow(penguins)` rows.
# The mean is `round(mean(x, na.rm = TRUE), 1)`.
# Analysis run on `Sys.Date()`.
```
 
example with palmer penguins package
```{r}
#load libaries
library(palmerpenguins)
library(tidyverse)
```
 
 The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 
 
 The mean bill length of penguins is `r round(mean(penguins$bill_length_mm, na.rm=TRUE))` millimeters.
 
 also always use the here function with quarto docs
 
## Publishing the quarto doc with posit connect cloud 
Anyone with the link can view the doc, and everytime you re-publish the link stays the same
How we will submit the homework!


## Lecture pt 2

Working with figures, you can change the size, resolution, file type, etc. 
For practice, make a simple penguin plot
```{r}
pplot <- ggplot(penguins,
                mapping = aes(x=bill_length_mm, y=bill_depth_mm, color=species)) +
  geom_point() +
  labs(x="Bill Length (mm)", y="Bill Depth (mm)", title = "Bill Length and Depth of Adelie, Chinstrap, and Gentoo Penguins")

 
```

 
How to cross reference figures in your quarto script and linkable in your prose

step 1: Give your chunk a label starting with fig-
```{r}
#| label: fig-penguin-bill
#| fig-cap: "Bill length vs Bill depth for three penguin species"
#| echo: false

ggplot(penguins, 
       mapping = aes(x=bill_length_mm, y=bill_depth_mm, color=species)) +
  geom_point() +
  labs(x="Bill Length (mm)", y="Bill Depth (mm)", title = "Bill Length and Depth of Adelie, Chinstrap, and Gentoo Penguins")

```
 
 you can reference this figure anywhere in your prose by: @the figure label 
 
 As shown in @fig-penguin-bill, bill dimensions differ clearly by species.
 
 You can do the same with tables, where label must start with tbl-, use package kableExtra
```{r}
#| label: tbl-penguin-means
#| tbl-cap: "Mean bill length by species."

library(kableExtra)

penguins |>
  group_by(species) |>
  summarise(mean_bill = mean(bill_length_mm, na.rm = TRUE)) |>
  kbl()
```
 Then you can reference in your prose like this:
 
 Mean bill lengths are summarised in @tbl-penguin-means.
 
 
 To show your code in your output, or to toggle it on and off, you can use cold-fold
---
title: "My Analysis"
format:
  html:
    code-fold: true              # code hidden by default, with a toggle button
    code-summary: "Show code"    # customize the button label
---